---
title: "p8105_hw5_js5959"
author: "Junzhe Shao"
date: "11/20/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(broom)
```
## Problem 1

```{r }
homicide_data_raw <- read_csv("homicide-data.csv", na = c("","unknown"))
```

Data has `r nrow(homicide_data_raw)` observations. number of variables is `r ncol(homicide_data_raw)` , and they are `r colnames(homicide_data_raw)`.


```{r }

homicide_data_process <- homicide_data_raw %>%
  mutate(
    city_state = paste(city,state)
  )
homicide_dt <- homicide_data_process %>%
  group_by(city_state) %>%
  summarize(
    homicide = n(),
    disposition = disposition
  ) %>%
  filter(disposition %in% c("Closed without arrest","Open/No arrest")) %>%
  group_by(city_state) %>%
  summarize(
    unsolved = n(),
    homicide = homicide
  ) %>%
  distinct()
homicide_dt
```


```{r }
baltimore_dt <- homicide_dt %>%
  filter(city_state == "Baltimore MD")
baltimore_prop_test <- prop.test(pull(baltimore_dt,unsolved),pull(baltimore_dt,homicide))
broom::tidy(baltimore_prop_test)
```

```{r }
city_dt <- homicide_dt %>%
  mutate(
    prop_test = map2(unsolved, homicide, prop.test),
    prop_test = map(prop_test, broom::tidy)
  ) %>%
  unnest(cols = prop_test) %>%
  select(city_state,estimate,conf.low,conf.high)
city_dt
```

```{r }
city_dt %>%
  arrange(estimate) %>%
  ggplot(aes(x = fct_reorder(city_state,estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    x = "City",
    y = "Estimate"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

  
## Problem 2
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
```{r}
filenames = tibble(list.files(path = "./data"),)
read_list <- function(x){
  file = paste("./data/",x, sep = "")
  print(file)
  read_csv(file) %>% 
    mutate(name = x, .before=week_1)
}

test <- bind_rows(map(.x = filenames, read_list)) %>%
      rowwise() %>% 
      mutate(exp_cont = str_split(name,"_")[[1]][1],
           subject_ID = str_split(str_split(name,"_")[[1]][2],"[.]")[[1]][1], .after = name,
           exp_ID = str_split(name,"[.]")[[1]][1])

plot_dt = pivot_longer(test,
                        week_1:week_8,
                        names_to = "week",
                        names_prefix = "week_",
                        values_to = "observation")

plot_dt %>% group_by(exp_ID) %>% ggplot(aes(x = week, y = observation, group = exp_ID, color = exp_cont))+geom_line(size =1)
```

We can see experiment arm has an increasing trend while control arms has no clear trend. experiment arm observation is larger than control arm in general.  

## Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

fill_missing <- function(x){
  if(is.numeric(x)){
    x = ifelse(is.na(x), mean(x, na.rm = T), x)
  }
  else if(is.character(x)){
    x = ifelse(is.na(x), "virginica",x)
  }
}
  
fill_dt <- map_df(iris_with_missing,fill_missing)

fill_dt
```
 
